---
title: "Insights"
date: "`r Sys.Date()`"
format: 
  html:
    embed-resources: true
    number-sections: true
    code-fold: true
    toc: true
editor: source
---

```{r}
#| include: false

knitr::opts_chunk$set(warning = FALSE, message = FALSE)

library(tidyverse)

```


# Gender representation in sessions (descriptive)

Descriptive representation of women around 25% across sessions and doesn't shift that much across parliaments.

```{r}

# read data

# get attendance data

attn_df <- read.csv("cleaned_output/attendance.csv")

gender_prop <- 
  attn_df %>% 
  mutate(female = ifelse(Gender=="F", 1, 0),
         parl_session = paste0(parl, "_", Date)) %>% 
  group_by(parl, parl_session) %>% 
  summarise(female_prop = mean(female)) %>% 
  mutate(parliament = factor(parl))

gender_prop %>% 
  ggplot(aes(female_prop, fill = parliament)) +
  geom_histogram(binwidth = .01) +
  ggtitle("Histogram of parliament attendance by gender, grouped by parliament")


```


# Number of speeches and duration

Men speak slightly more than women even after accounting for gender imbalance (inverse weighted). 14th parliament more skewed.

```{r}
# first clean some data

all_df <- read_csv("cleaned_output/cleaned_speeches.csv")

# filter out all speeches that are questions and only include speeches whose lengths are between 10 and 90 percentile

quantiles <- 
  quantile(all_df$word_count, probs = seq(0,1,0.1))[c(2,10)]

all_df <- 
  all_df %>% 
  filter(!grepl("^(a|A)sk", Text) & 
           between(word_count, quantiles[1], quantiles[2])) %>% 
  mutate(parliament = factor(parl))


```


```{r}

# how often do people speak?

# we inverse weight by gender proportion

weight_df <- 
  gender_prop %>% 
  rename(weight = female_prop) %>% 
  group_by(parl_session) %>% 
  slice(rep(1, 2)) %>% 
  mutate(weight = c(weight[1], 1-weight[1]),
         Gender = c("M", "F"))

# calculate nunber of times each gender spoke within a session

df_speak <- 
  all_df %>% 
  group_by(parl, parl_session, Gender) %>% 
  summarise(n_speak = n())

# now inverse weight by gender proportion for that session

df_speak <- 
  df_speak %>% 
  left_join(weight_df) %>% 
  mutate(n_speak = n_speak*weight)

df_speak %>% 
  ggplot(aes(n_speak, fill = Gender)) +
  geom_density(alpha = 0.5) +
  facet_wrap(~parliament, ncol = 2, scales = "free") +
  theme_minimal() +
  ggtitle("Density plot of number of times people speak, faceted by parliament",
          subtitle = "n_speak is inverse weighted by the gender proportion for that parliamentary session")

```


In addition to how many times parliamentarians speak, we can also plot how long speeches are. We see that speech lengths across genders are very similar.

```{r}

# what do speech lengths look like?

all_df %>% 
  ggplot(aes(word_count, fill = Gender)) +
  geom_density(alpha = 0.5) +
  ggtitle("Density plot of word length of speeches")

```

